Supplementary Material for 'New insights into the Weddell Sea ecosystem applying

### 2023-11-06 Manuscript/SupMaterial.Rmd
Corrections to all_dif dataframe for the SI table

load("QSS_summary_sep22.rda")
knitr::kable(all_data %>% dplyr::select(TrophicSpecies, QSS_all, QSS_ext, difQSS, Ad_pvalue) %>% arrange(., Ad_pvalue), digits = c(0,7,7,7,41), col.names = c("Species", "QSS_all", "QSS_ext", "difQSS", "AD_pvalue"), caption = "Summary of Quasi-Sign Stability (QSS) results before and after performing extinction simulations in the Weddell Sea food web. Ordered by increasing p-values of the Anderson-Darling test. QSS_all = Mean Quasi-Sign Stability before the extinction (whole food web), QSS_ext = Mean Quasi-Sign Stability after the extinction, difQSS = QSS difference between 'QSS_all' and 'QSS_ext', AD_pvalue = p-value for the Anderson-Darling test.")

>>>>

load("../Results/QSS_summary_oct31.rda")
knitr::kable(all_dif %>% dplyr::select(TrophicSpecies, prop_difQSSm_pos, prop_difQSSm_neg, median_difQSS) %>% arrange(., prop_difQSSm_neg), digits = c(0,7,7,7,41), col.names = c("Species", "Prop dif QSS +", "Prop dif QSS - ", "Median difQSS relat"), caption = "Summary of Maximum eigenvalue (QSS) distribution of differences before and after performing extinction simulations in the Weddell Sea food web. Ordered by increasing proportion of positive differences. Prop dif QSS +  = Proportion of positive differences, Prop dif QSS - = Proportion of negative differences, Median difQSS relat = median of QSS differences")
